\thetitle

### 2008-05-21 paper.tex
Finally found Springer journal format LaTeX files.
  - still complains about lots of fonts
  - also deleted .texshop files--using TextMate
  - deleted old IEEE format files

\documentclass[conference]{IEEEtran}

\newcommand{\thetitle}{An Algebraic Representation of Wireless Workload}

\usepackage[pdftex]{graphicx}
\usepackage[labelfont=bf,small]{caption}
\usepackage[font=small,labelfont=bf,position=top,nearskip=0em]{subfig}
\usepackage{cite,amsmath,amssymb,rotating,multirow,bigstrut,url,wrapfig}
\usepackage[hyperfigures,bookmarks,bookmarksopen,bookmarksnumbered,colorlinks,linkcolor=black,citecolor=black,filecolor=blue,menucolor=black,pagecolor=blue,frenchlinks=true,pdftitle={\thetitle}]{hyperref}
\usepackage{array}

\hyphenation{net-works IEEEtran}
\bibliographystyle{IEEEtran}

\newcommand{\email}[1]{$\left<{\textit{#1}}\right>$}
\newcommand{\caps}[1]{{\small{#1}}}

\title{An Algebraic Representation of Wireless Workload}
\author{
{\large{Stefan~Karpinski, Elizabeth~M.~Belding, Kevin~C.~Almeroth}}\\
\textit{\{sgk,ebelding,almeroth\}@cs.ucsb.edu}\vspace{0.5em}\\
Department of Computer Science\\
University of California, Santa Barbara
\vspace{-0.5em}
}

@@

\newcommand{\figurename}{Figure}
\newcommand{\tablename}{Table}

@@

\vspace{-0.5em}
\appendix\footnotesize

\noindent
\textbf{Theorem.} The unique differentiable function satisfying Eqs.~\ref{eqn:normalization-invariance}~\&~\ref{eqn:linear-compounding} is $E(1,e) \ln(y/x)$. \textit{Proof:} Let $f(z) = E(1,z)$. Eq.~\ref{eqn:normalization-invariance} gives $E(x,y) = E(1,y/x) = f(y/x)$. Eq.~\ref{eqn:linear-compounding} gives: $f(z) = f(z/w) + f(w)$. Differentiation by $z$ yields $f'(z) = w^{-1} f'(z/w)$. In particular, if we choose $w=z$, we get $f'(z) = z^{-1} f'(1)$. Integration by $z$ gives:
$f(z) = f'(1) \int z^{-1} dz + c = f'(1) \ln(z) + c$.
By Eq.~\ref{eqn:linear-compounding}, $f(1)=0$, so $c=0$. Thus $f(e)=f'(1)\ln(e)=f'(1)$. We conclude that $f(z)=f(e)\ln(z)$, so $E(x,y) = f(y/x) = f(e)\ln(y/x) = E(1,e)\ln(y/x)$, as desired.\hfill\QED

>>>>

\documentclass[twocolumn,final]{svjour3}

\newcommand{\thetitle}{An Algebraic Representation of Wireless Workload}
\newcommand{\theauthors}{%
  Stefan~Karpinski \and
  Elizabeth~M.~Belding \and
  Kevin~C.~Almeroth \and
  John~R.~Gilbert%
}

%\usepackage[pdftex]{graphicx}
\usepackage[labelfont=bf,small]{caption}
\usepackage[font=small,labelfont=bf,position=top,nearskip=0em]{subfig}
\usepackage{cite,amsmath,amssymb,rotating,multirow,bigstrut,url,wrapfig}
\usepackage[hyperfigures,bookmarks,bookmarksopen,bookmarksnumbered,colorlinks,linkcolor=black,citecolor=black,filecolor=blue,menucolor=black,pagecolor=blue,frenchlinks=true,pdftitle={\thetitle}]{hyperref}
\usepackage{array}

\newcommand{\caps}[1]{{\small{#1}}}

\title{\thetitle}
\author{\theauthors}
\institute{
  \theauthors\\
  Department of Computer Science\\
  University of California, Santa Barbara\\
  Email: \texttt{\{sgk,ebelding,almeroth,gilbert\}@cs.ucsb.edu}
}

@@

@@

\section*{Appendix}
\footnotesize

\noindent
\textbf{Theorem.} The unique differentiable function satisfying Eqs.~\ref{eqn:normalization-invariance}~\&~\ref{eqn:linear-compounding} is $E(1,e) \ln(y/x)$. \textit{Proof:} Let $f(z) = E(1,z)$. Eq.~\ref{eqn:normalization-invariance} gives $E(x,y) = E(1,y/x) = f(y/x)$. Eq.~\ref{eqn:linear-compounding} gives: $f(z) = f(z/w) + f(w)$. Differentiation by $z$ yields $f'(z) = w^{-1} f'(z/w)$. In particular, if we choose $w=z$, we get $f'(z) = z^{-1} f'(1)$. Integration by $z$ gives:
$f(z) = f'(1) \int z^{-1} dz + c = f'(1) \ln(z) + c$.
By Eq.~\ref{eqn:linear-compounding}, $f(1)=0$, so $c=0$. Thus $f(e)=f'(1)\ln(e)=f'(1)$. We conclude that $f(z)=f(e)\ln(z)$, so $E(x,y) = f(y/x) = f(e)\ln(y/x) = E(1,e)\ln(y/x)$, as desired.\hfill%\QED
